Manuscript

### 2015-01-10 inst/simulation/manuscript.Rmd
..

prettyModelName <- function(x) {
  lookup <- data.frame(x=c("SmoothModel-nbinomial-matern-ar1", "SmoothModel-nbinomial-ar1", "FMPModel") , y=c("ST", "T", "I"), stringsAsFactors=F)
  lookup$y[match(x, lookup$x)]
}

@@

```{r figure-1}
habitatRaster <- crop(study$studyArea$habitat, extent(c(3.375, 3.4, 6.9, 6.925)*1e6))
z <- sampleRegular(habitatRaster, 10000, asRaster=TRUE)
habitatData <- as.data.frame(rasterToPoints(z))
#habitatData <- as.data.frame(rasterToPoints(habitatRaster))
colnames(habitatData) <- c("x","y","z")
habitatData$scenario <- factor("E", levels=scenarios)
habitatData2 <- habitatData
habitatData2$scenario <- factor("F", levels=scenarios)
habitatData <- rbind(habitatData, habitatData2)

@@

p <- ggplot(habitatData) + geom_raster(aes(x, y, fill=z)) + scale_fill_manual(values=col) +
  geom_path(data=trackData, aes(long, lat, group=group, colour=observation)) +#, alpha=observation)) +
  scale_colour_manual(values=c("gray40","black")) +# scale_alpha_manual(values=c(.5,1)) +
  geom_path(data=surveyRoutesData, aes(long, lat, group=group)) +
  coord_fixed(ratio=1, xlim=c(3.375,3.4)*1e6, ylim=c(6.9,6.925)*1e6) +
  facet_wrap(~scenario) + #coord_equal()
  theme_raster(base_size=10) + theme(panel.border=element_rect(fill="transparent"))
#print(p)
saveFigure(p, "manuscript-figure-1.png", width=8, height=4)

getRaster <- function(habitatRaster, xlim, ylim, size=10000) {
  x <- crop(habitatRaster, extent(c(xlim, ylim)))
  y <- sampleRegular(x, size=size, asRaster=TRUE)
  habitatData <- as.data.frame(rasterToPoints(y))
  colnames(habitatData) <- c("x","y","z")
  habitatData$z <- factor(habitatData$z, levels=0:255)
  col <- habitatRaster@legend@colortable
  names(col) <- 0:255
  return(habitatData)
}

@@

getEstimatedDensity = function(scenarios, modelName, iterations, year, sd=FALSE) {
  ddply(data.frame(scenario=scenarios, iteration=iterations, stringsAsFactors=FALSE), .(scenario, iteration), function(x, modelName, year0, sd) {
    message("Scenario = ", x$scenario, ", iteration = ", x$iteration)
    study <- getStudy(scenario=x$scenario)
    estimates <- study$getModel(modelName=modelName, iteration=x$iteration)
    estimates$modelName <- modelName
    estimates <- study$loadEstimates(estimates)
    estimates$collectEstimates()

    estimates$data <- subset(estimates$data, year == year0)
    density <- estimates$getPopulationDensity(getSD=sd)
    density <- if (sd) density$sd else density$mean
    if (is.null(density) || maxValue(density$rasterStack[[1]]) > 1) stop("Estimation failed.")
    density <- as.data.frame(density$rasterStack[[1]], xy=T)
    density$Scenario <- x$scenario
    density$Iteration <- x$iteration
    density$Model <- modelName
    density$Year <- year0

@@

```{r figure-2-test}
iterations <- as.integer(c(1,1,3,2,5,6))
year <- 2010
surveyRoutes <- getSurveyRouteLocations(scenarios=scenarios[1], modelName=modelNames[1], iterations=iterations[1], years=year)
surveyRoutes <- rbind(surveyRoutes[surveyRoutes$Intersection == FALSE,], surveyRoutes[surveyRoutes$Intersection == TRUE,])
agents <- getAgentLocations(scenarios=scenarios[1], modelName=modelNames[1], iterations=iterations[1], years=year)
densityST <- getEstimatedDensity(scenarios[1], modelNames[1], iterations[1], year=year, sd=FALSE)
densityFMP <- getEstimatedDensity(scenarios[1], modelNames[3], iterations[1], year=year, sd=FALSE)
limits <- extent(study$studyArea$boundary)

@@

```{r figure-2}
iterations <- as.integer(c(1,1,3,2,5,6))
#iterations <- as.integer(c(1,1,3,2,5,7))
year <- 2010
yearLayer <- paste0("X", year)
surveyRoutes <- getSurveyRouteLocations(scenarios=scenarios, modelName=modelNames[1], iterations=iterations, years=year)
surveyRoutes <- rbind(surveyRoutes[surveyRoutes$Intersection == FALSE,], surveyRoutes[surveyRoutes$Intersection == TRUE,])
agents <- getAgentLocations(scenarios=scenarios, modelName=modelNames[1], iterations=iterations, years=year)
densities <- getEstimatedDensity(scenarios=scenarios, modelName=modelNames[1], iterations=iterations, year=year, sd=F)
# TODO: do not use scaling??
densitiesScaled <- ddply(densities, .(scenario), function(x, yearLayer) { x[,yearLayer] <- scale(x[,yearLayer]); return(x) }, yearLayer=yearLayer)
limits <- extent(study$studyArea$boundary)

#p <- ggplot(boundaryDF) + geom_polygon(aes(long, lat, group=group), fill=terrain.colors(100)[1]) +
p <- ggplot(densitiesScaled) + geom_raster(aes_string(x="x", y="y", fill=yearLayer)) + scale_fill_gradientn(colours=terrain.colors(100), na.value="transparent") +
  geom_path(data=boundaryDF, aes(long, lat, group=group), colour="darkgreen") +
  geom_point(data=agents, aes(x, y, colour=Observed), size=1) + scale_color_manual(values=c("darkgray", "black")) + 
  scale_x_continuous(limits=c(limits@xmin, limits@xmax), expand=c(0,0)) +
  scale_y_continuous(limits=c(limits@ymin, limits@ymax), expand=c(0,0)) +
  facet_grid(~scenario) + theme_raster(base_size=10) + coord_equal()
print(p)
saveFigure(p, "manuscript-figure-2a.png", width=8)

@@

getMeanPopulationSizes <- function(populationSizes) {
  meanPopulationSizes <- ddply(populationSizes, .(scenario, modelName), function(x) {
    data.frame(True=mean(x$Observed), Estimated=mean(x$Estimated), Scenario=x$scenario)
  })
  return(meanPopulationSizes)
}

getLogPopulationSizes <- function(populationSizes) {
  logPopulationSizes <- populationSizes
  logPopulationSizes$Observed <- logPopulationSizes$Observed + 1
  logPopulationSizes$Estimated <- logPopulationSizes$Estimated + 1
  return(logPopulationSizes)
}

getLogMeanPopulationSizes <- function(populationSizes) {  
  logMeanPopulationSizes <- ddply(populationSizes, .(scenario, modelName), function(x) {
    data.frame(True=10^mean(log10(x$Observed+1)), Estimated=10^mean(log10(x$Estimated+1)), Scenario=x$scenario)
  })
  return(logMeanPopulationSizes)
}

plotLogPopulationSize <- function(size, meanSize, modelName, xlim, ylim) {
  library(ggplot2)
  library(scales)  
  p <- ggplot(size, aes(Observed, Estimated, colour=modelName)) +
    #geom_point(size=1) +
    #stat_smooth(method="lm", aes(colour=modelName), se=F) +
    geom_point(size=1, colour="darkgray") +
#stat_smooth(method="lm", se=F, colour="black") +
    #scale_colour_manual("Model", values=c("lightgray", "darkgray","black"), labels=c("I", "T", "ST")) +
    #scale_colour_manual("Model", values=c("darkgray","black")) +
    geom_abline(colour="black", linetype="longdash") + 
    #geom_point(data=meanSize, aes(True, Estimated, colour=modelName), size=2, shape=15) +
    geom_point(data=meanSize, aes(True, Estimated), size=2, shape=15, colour="black") +
    facet_wrap(~Scenario, scales="free") +
    coord_cartesian(xlim=xlim, ylim=ylim) +
    scale_x_log10() + scale_y_log10() +
    xlab("True population size") + ylab("Estimated population size") + ggtitle(paste("Model: ", prettyModelName(modelName[1]))) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"), legend.title=element_text(size=12))

  if (!any(abs(size$Estimated) == Inf)) p <- p + stat_smooth(method="lm", se=F, colour="black")

  print(p)
  return(p)
}
```

@@

meanPopulationSizes  <- getMeanPopulationSizes(populationSizes)
logPopulationSizes <- getLogPopulationSizes(populationSizes)
logMeanPopulationSizes  <- getLogMeanPopulationSizes(populationSizes)

meanPopulationSizes2000  <- getMeanPopulationSizes(populationSizes2000)
logPopulationSizes2000 <- getLogPopulationSizes(populationSizes2000)
logMeanPopulationSizes2000  <- getLogMeanPopulationSizes(populationSizes2000)

meanPopulationSizes10Days  <- getMeanPopulationSizes(populationSizes10Days)
logPopulationSizes10Days <- getLogPopulationSizes(populationSizes10Days)
logMeanPopulationSizes10Days  <- getLogMeanPopulationSizes(populationSizes10Days)
#validation$summarizePopulationSize(populationSizes10Days)
```

```{r figure-3abc}
p <- plotLogPopulationSize(subset(logPopulationSizes, modelName==modelNames[1]), subset(logMeanPopulationSizes, modelName==modelNames[1]), modelName=modelNames[1], xlim=c(1,10000), ylim=c(1,10000))
saveFigure(p, "manuscript-figure-3a1.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes, modelName==modelNames[2]), subset(logMeanPopulationSizes, modelName==modelNames[2]), modelName=modelNames[2], xlim=c(1,10000), ylim=c(1,10000))
saveFigure(p, "manuscript-figure-3a2.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes, modelName==modelNames[3]), subset(logMeanPopulationSizes, modelName==modelNames[3]), modelName=modelNames[3], xlim=c(1,10000), ylim=c(1,10000))
saveFigure(p, "manuscript-figure-3a3.png", width=8, height=4)

xlim <- c(100,10000)
ylim <- xlim
p <- plotLogPopulationSize(subset(logPopulationSizes2000, modelName==modelNames[1]), subset(logMeanPopulationSizes2000, modelName==modelNames[1]), modelName=modelNames[1], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3b1.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes2000, modelName==modelNames[2]), subset(logMeanPopulationSizes2000, modelName==modelNames[2]), modelName=modelNames[2], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3b2.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes2000, modelName==modelNames[3]), subset(logMeanPopulationSizes2000, modelName==modelNames[3]), modelName=modelNames[3], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3b3.png", width=8, height=4)

p <- plotLogPopulationSize(subset(logPopulationSizes10Days, modelName==modelNames[1]), subset(logMeanPopulationSizes10Days, modelName==modelNames[1]), modelName=modelNames[1], xlim=c(1,10000), ylim=c(1,10000))
saveFigure(p, "manuscript-figure-3c1.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes10Days, modelName==modelNames[2]), subset(logMeanPopulationSizes10Days, modelName==modelNames[2]), modelName=modelNames[2], xlim=c(1,10000), ylim=c(1,10000))
saveFigure(p, "manuscript-figure-3c2.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes10Days, modelName==modelNames[3]), subset(logMeanPopulationSizes10Days, modelName==modelNames[3]), modelName=modelNames[3], xlim=c(1,10000), ylim=c(1,10000))
saveFigure(p, "manuscript-figure-3c3.png", width=8, height=4)
```

@@

dir <- normalizePath(context$figuresDirectory)
getPopulationSizesTable(populationSizes, meanPopulationSizes, file=file.path(dir, "table-1a.csv"))
getPopulationSizesTable(populationSizes2000, meanPopulationSizes2000, file=file.path(dir, "table-1b.csv"))
getPopulationSizesTable(populationSizes10Days, meanPopulationSizes10Days, file=file.path(dir, "table-1c.csv"))
```

>>>>

prettyScenario <- function(scenario) substr(scenario, 1, 1)
prettyModelName <- function(x) {
  lookup <- data.frame(x=c("SmoothModel-nbinomial-matern-ar1", "SmoothModel-nbinomial-ar1", "FMPModel") , y=c("ST", "T", "I"), stringsAsFactors=F)
  lookup$y[match(x, lookup$x)]
}

@@

```{r figure-1}
#window <- c(3.375, 3.4, 6.9, 6.925)*1e6
window <- (c(3.375, 3.4, 6.9, 6.925)+c(-.01,.01,-.01,.01)*3)*1e6
habitatRaster <- crop(study$studyArea$habitat, extent(window))
z <- sampleRegular(habitatRaster, 10000, asRaster=TRUE)
habitatData <- as.data.frame(rasterToPoints(z))
#habitatData <- as.data.frame(rasterToPoints(habitatRaster))
colnames(habitatData) <- c("x","y","z")
habitatData$scenario <- factor("E", levels=scenarios)
habitatData2 <- habitatData
habitatData2$scenario <- factor("F", levels=scenarios)
habitatData <- rbind(habitatData, habitatData2)

@@

p <- ggplot(habitatData) + geom_raster(aes(x, y, fill=z), alpha=.3) + scale_fill_manual(values=col) +
  geom_path(data=trackData, aes(long, lat, group=group, colour=observation), alpha=1, size=.3) +#, alpha=observation)) +
  scale_colour_manual(values=c("darkgray","black")) + # scale_alpha_manual(values=c(.5,1)) + # gray40
  geom_path(data=surveyRoutesData, aes(long, lat, group=group), size=.3, colour="blue", alpha=.5) +
  coord_fixed(ratio=1, xlim=window[1:2], ylim=window[3:4]) +
  facet_wrap(~scenario) + #coord_equal()
  theme_raster(base_size=10) + theme(panel.border=element_rect(fill="transparent"))
#print(p)
saveFigure(p, "manuscript-figure-1.png", width=8, height=4)

# scale on the map in km
c((window[2]-window[1]), (window[4]-window[3]))/1000
```

```{r figure-1-separate, eval=FALSE}
getRaster <- function(habitatRaster, xlim, ylim, size=10000) {
  x <- crop(habitatRaster, extent(c(xlim, ylim)))
  y <- sampleRegular(x, size=size, asRaster=TRUE)
  habitatData <- as.data.frame(rasterToPoints(y))
  colnames(habitatData) <- c("x","y","z")
  habitatData$z <- factor(habitatData$z, levels=0:255)
  col <- habitatRaster@legend@colortable
  names(col) <- 0:255
  return(habitatData)
}

@@

getEstimatedDensity = function(scenarios, modelName, iterations, year, sd=FALSE, log=FALSE) {
  ddply(data.frame(scenario=scenarios, iteration=iterations, stringsAsFactors=FALSE), .(scenario, iteration), function(x, modelName, year0, sd) {
    message("Scenario = ", x$scenario, ", iteration = ", x$iteration)
    study <- getStudy(scenario=x$scenario)
    estimates <- study$getModel(modelName=modelName, iteration=x$iteration)
    estimates$modelName <- modelName
    estimates <- study$loadEstimates(estimates)
    estimates$collectEstimates()

    studyArea <- FinlandStudyArea$new(context=context)$setup(tolerance=0.001)

    estimates$data <- subset(estimates$data, year == year0)
    if (log) estimates$data$fittedMean <- log(estimates$data$fittedMean)
    density <- estimates$getPopulationDensityInterpolate(getSD=sd, maskPolygon=studyArea$boundary)
    density <- if (sd) density$sd else density$mean
    if (is.null(density) || maxValue(density$rasterStack[[1]]) > 1) stop("Estimation failed.")
    density <- as.data.frame(density$rasterStack[[1]], xy=T)
    density$Scenario <- x$scenario
    density$Iteration <- x$iteration
    density$Model <- modelName
    density$Year <- year0

@@

```{r figure-2-test}
iterations <- as.integer(c(1,1,3,2,5,6))
year <- 2010
densityST <- getEstimatedDensity(scenarios[1], modelNames[1], iterations[1], year=year, sd=FALSE)
p <- ggplot(densityST) + geom_raster(aes_string(x="x", y="y", fill=paste0("X", year))) + scale_fill_gradientn(colours=terrain.colors(100), na.value="transparent") 
saveFigure(p, "tmp_compare_densities_ST.png", width=8)
###

iterations <- as.integer(c(1,1,3,2,5,6))
year <- 2010
surveyRoutes <- getSurveyRouteLocations(scenarios=scenarios[1], modelName=modelNames[1], iterations=iterations[1], years=year)
surveyRoutes <- rbind(surveyRoutes[surveyRoutes$Intersection == FALSE,], surveyRoutes[surveyRoutes$Intersection == TRUE,])
agents <- getAgentLocations(scenarios=scenarios[1], modelName=modelNames[1], iterations=iterations[1], years=year)
densityST <- getEstimatedDensity(scenarios[1], modelNames[1], iterations[1], year=year, sd=FALSE)
densityFMP <- getEstimatedDensity(scenarios[1], modelNames[3], iterations[1], year=year, sd=FALSE)
limits <- extent(study$studyArea$boundary)

@@

```{r figure-2}
#iterations <- as.integer(c(1,1,3,2,5,6))
##iterations <- as.integer(c(1,1,3,2,5,7))
iterations <- as.integer(c(1,1,3,2,5,8))
year <- 2010
yearLayer <- paste0("X", year)
surveyRoutes <- getSurveyRouteLocations(scenarios=scenarios, modelName=modelNames[1], iterations=iterations, years=year)
surveyRoutes <- rbind(surveyRoutes[surveyRoutes$Intersection == FALSE,], surveyRoutes[surveyRoutes$Intersection == TRUE,])
agents <- getAgentLocations(scenarios=scenarios, modelName=modelNames[1], iterations=iterations, years=year)
densities <- getEstimatedDensity(scenarios=scenarios, modelName=modelNames[1], iterations=iterations, year=year, sd=F, log=T)
# TODO: do not use scaling??
#densitiesScaled <- ddply(densities, .(scenario), function(x, yearLayer) { x[,yearLayer] <- scale(x[,yearLayer]); return(x) }, yearLayer=yearLayer)
study <- getStudy(scenario="A")
limits <- extent(study$studyArea$boundary)

# Scale density to 1/km^2
densitiesScaled <- ddply(densities, .(scenario), function(x, yearLayer, weight) {
  x[,yearLayer] <- x[,yearLayer] * weight
  return(x)
}, yearLayer=yearLayer, weight=1 / (prod(res(study$getTemplateRaster())) / 1000^2))

#p <- ggplot(boundaryDF) + geom_polygon(aes(long, lat, group=group), fill=terrain.colors(100)[1]) +
p <- ggplot(densitiesScaled) + geom_raster(aes_string(x="x", y="y", fill=yearLayer)) +
  scale_fill_gradientn(colours=terrain.colors(100), na.value="transparent", guide=guide_legend(title=expression(paste("Density ", individuals/km^2)))) +
  geom_path(data=boundaryDF, aes(long, lat, group=group), colour="darkgreen") +
  geom_point(data=agents, aes(x, y, colour=Observed), size=1) + scale_color_manual(values=c("darkgray", "black"), guide=FALSE) + 
  scale_x_continuous(limits=c(limits@xmin, limits@xmax), expand=c(0,0)) +
  scale_y_continuous(limits=c(limits@ymin, limits@ymax), expand=c(0,0)) +
  facet_grid(~scenario) + coord_equal() + theme_raster(base_size=10) + theme(legend.position="bottom")
print(p)
saveFigure(p, "manuscript-figure-2a.png", width=8)

###

@@

getMeanPopulationSizes <- function(populationSizes) {
  meanPopulationSizes <- ddply(populationSizes, .(scenario, modelName), function(x) {
    x <- data.frame(True=mean(x$Observed), Estimated=mean(x$Estimated), Scenario=x$scenario[1])
    if (is.infinite(x$True)) x$True <- NA
    if (is.infinite(x$Estimated)) x$Estimated <- NA
    return(x)
  })
  return(meanPopulationSizes)
}

getLogPopulationSizes <- function(populationSizes) {
  logPopulationSizes <- populationSizes
  logPopulationSizes$Observed <- log10(logPopulationSizes$Observed + 1)
  logPopulationSizes$Estimated <- log10(logPopulationSizes$Estimated + 1)
  return(logPopulationSizes)
}

plotLogPopulationSize <- function(size, meanSize, modelName, xlim, ylim) {
  library(ggplot2)
  library(scales)  
  size$Scenario <- prettyScenario(size$Scenario)
  meanSize$Scenario <- prettyScenario(meanSize$Scenario)

  p <- ggplot(size, aes(Observed, Estimated, colour=modelName)) +
    geom_point(size=1, colour="darkgray", alpha=.25) +
    geom_abline(colour="black", linetype="longdash") + 
    geom_point(data=meanSize, aes(True, Estimated), size=2, shape=15, colour="black")

  #if (!any(abs(size$Estimated) == Inf)) p <- p + geom_smooth(method="lm", se=F, fullrange=T, colour="black")
  ls <- ddply(size, .(Scenario), function(x) if (!any(abs(x$Estimated) == Inf)) coef(lm(Estimated~Observed, x)) else c(NA,NA))
  p <- p + geom_abline(data=ls, aes(intercept=`(Intercept)`, slope=Observed))

  p <- p + facet_wrap(~Scenario) +
    scale_x_continuous(limits=xlim, labels=trans_format("identity", math_format(10^.x))) +
    scale_y_continuous(limits=ylim, labels=trans_format("identity", math_format(10^.x))) +
    xlab("True population size") + ylab("Estimated population size") + ggtitle(paste("Model: ", prettyModelName(modelName[1]))) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent"), legend.title=element_text(size=12))

  print(p)
  return(p)
}

#p <- plotLogPopulationSize(subset(logPopulationSizes, modelName==modelNames[1]), subset(logMeanPopulationSizes, modelName==modelNames[1]), modelName=modelNames[1], xlim=xlim, ylim=ylim)
#saveFigure(p, "manuscript-figure-3a1.png", width=8, height=4)

#xlim <- log10(10^c(0,6)); ylim <- xlim
#p <- plotLogPopulationSize(subset(logPopulationSizes10Days, modelName==modelNames[2]), subset(logMeanPopulationSizes10Days, modelName==modelNames[2]), modelName=modelNames[2], xlim=xlim, ylim=ylim)
#saveFigure(p, "manuscript-figure-3c2.png", width=8, height=4)
```

@@

meanPopulationSizes  <- getMeanPopulationSizes(populationSizes)
logPopulationSizes <- getLogPopulationSizes(populationSizes)
logMeanPopulationSizes  <- getMeanPopulationSizes(logPopulationSizes)

meanPopulationSizes2000  <- getMeanPopulationSizes(populationSizes2000)
logPopulationSizes2000 <- getLogPopulationSizes(populationSizes2000)
logMeanPopulationSizes2000  <- getMeanPopulationSizes(logPopulationSizes2000)

meanPopulationSizes10Days  <- getMeanPopulationSizes(populationSizes10Days)
logPopulationSizes10Days <- getLogPopulationSizes(populationSizes10Days)
logMeanPopulationSizes10Days  <- getMeanPopulationSizes(logPopulationSizes10Days)
```

```{r figure-3abc}
xlim <- log10(10^c(0,4)); ylim <- xlim
p <- plotLogPopulationSize(subset(logPopulationSizes, modelName==modelNames[1]), subset(logMeanPopulationSizes, modelName==modelNames[1]), modelName=modelNames[1], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3a1.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes, modelName==modelNames[2]), subset(logMeanPopulationSizes, modelName==modelNames[2]), modelName=modelNames[2], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3a2.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes, modelName==modelNames[3]), subset(logMeanPopulationSizes, modelName==modelNames[3]), modelName=modelNames[3], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3a3.png", width=8, height=4)

xlim <- log10(10^c(2,4)); ylim <- xlim
p <- plotLogPopulationSize(subset(logPopulationSizes2000, modelName==modelNames[1]), subset(logMeanPopulationSizes2000, modelName==modelNames[1]), modelName=modelNames[1], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3b1.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes2000, modelName==modelNames[2]), subset(logMeanPopulationSizes2000, modelName==modelNames[2]), modelName=modelNames[2], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3b2.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes2000, modelName==modelNames[3]), subset(logMeanPopulationSizes2000, modelName==modelNames[3]), modelName=modelNames[3], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3b3.png", width=8, height=4)

xlim <- log10(10^c(0,4)); ylim <- xlim
p <- plotLogPopulationSize(subset(logPopulationSizes10Days, modelName==modelNames[1]), subset(logMeanPopulationSizes10Days, modelName==modelNames[1]), modelName=modelNames[1], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3c1.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes10Days, modelName==modelNames[2]), subset(logMeanPopulationSizes10Days, modelName==modelNames[2]), modelName=modelNames[2], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3c2.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes10Days, modelName==modelNames[3]), subset(logMeanPopulationSizes10Days, modelName==modelNames[3]), modelName=modelNames[3], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3c3.png", width=8, height=4)
```

@@

dir <- normalizePath(context$figuresDirectory)
getPopulationSizesTable(logPopulationSizes, logMeanPopulationSizes, file=file.path(dir, "table-1a.csv"))
getPopulationSizesTable(logPopulationSizes2000, logMeanPopulationSizes2000, file=file.path(dir, "table-1b.csv"))
getPopulationSizesTable(logPopulationSizes10Days, logMeanPopulationSizes10Days, file=file.path(dir, "table-1c.csv"))
```
